Automated verification of stand-alone solar photovoltaic systems

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%
%----------------------------------------
\section{Methodology }
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code. %\cite{ANSIC}.

>>>>

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%
%----------------------------------------
\section{Methodology }
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}.
